\documentclass[a4paper]{article}
\usepackage[letterpaper, margin=1in]{geometry} % page format
\usepackage{listings} % this package is for including code
\usepackage{graphicx} % this package is for including figures
\usepackage{amsmath}  % this package is for math and matrices
\usepackage{amsfonts} % this package is for math fonts
\usepackage{tikz} % for drawings
\usepackage{hyperref} % for urls

\title{Homework 00}
\author{Alex Palomba}
\date{9/5/16}

\begin{document}
\lstset{language=Python}

\maketitle

\section{Course Setup}

\subsection{Python Requirements}
Proof that I have successfully installed Python and all of the necessary packages is included in this folder as a screenshot titled $PythonProof.jpg$

\subsection{GitHub Class Repository}
My GitHub username is alexPalomba
Proof that I have added $pablorp80$ as a collaborator is included in this folder as a screenshot titled $GitHubProof.jpg$

\subsection{Kaggle Account}
My Kaggle username is alexPalomba; my display name is Plombo
Proof that I have created an account is included in this folder as a screenshot titled $KaggleProof.jpg$

\section{Problems}

\subsection{Problem 1}
g(x) = -3x^2_+24x - 30
Take the derivative and set to zero, then solve for x:
0 = -6x+24
24 = -6x
x = -4

\subsection{Problem 2}
I didn't understand how to do this one.

\subsection{Problem 3}
a) No you cannot. Matrices can only be multiplied if the number of columns in the first matrix is equal to the number of rows in the second matrix. 
b)I tried to figure out how to verify this in python and couldn't, but the answer is 
\begin{lstlisting}
> python hw1.7.1.py 
[(-4+0) (2+0) (6+0)]
[(-1+0) (-4+0) (3+0)]
[(14+0) (-9+0) (28-25)]
\end{lstlisting}

\begin{lstlisting}
> python hw1.7.1.py 
[(-4) (2) (6)]
[(-1) (-4) (3)]
[(14) (-9) (3)]
\end{lstlisting}

\subsection{Problem 4}
Simple Gaussian = a probability distribution that associates the normal random variable X with a cumulative probability. (Source: stattrek.com)
Multivariate Gaussian = a generalization of the one-dimensional normal distribution to higher dimensions. (Source: en.wikipedia.org)
Bernoulli = The Bernoulli distribution is a discrete distribution having two possible outcomes labelled by n=0 and n=1 in which n=1 ("success") 
occurs with probability  p and n=0 ("failure") occurs with probability q=1-p, where 0<p<1. (Source: mathworld.wolfram.com)
Binomial = a frequency distribution of the possible number of successful outcomes in a given number of trials in each of which there is the same probability of success. (Source: google search)
Exponential = is the probability distribution that describes the time between events in  
a process in which events occur continuously and independently at a constant average rate. It is a particular case of the gamma distribution. (Source: en.wikipedia.org)

\subsection{Problem 6}
I didn't understand how to do this one either.

\subsection{Problem 7}
a) given that the euclidean distance is the shortest distance between two points, if y is 1.1 then x* is 1 (the closest value within the set of all natural numbers). 
b) x* is the point on the edge of the circle closest to y.

\subsection{Problem 8}
I still don't understand how to do this one.


\section{Conclusions}
I'm honestly not sure if I did this assignment correctly, but I did my best - even if I couldn't answer all the questions (most of which were on material not covered in the prerequisite classes) and probably got most of the \LaTeX formatting wrong. Please let me know what I did wrong so I can hopefully improve on it in the future.


\end{document}
